\documentclass[oneside]{book}
\newcommand\deletechapter[1]{}

\title{Use Hostel}
\date{}
\author{\tiny
By Samuel Alexander\\\normalfont
\small
%\normalsize
    \parbox{0.8\linewidth}{\vspace{1in}In the year 2014 A.D.,
that is, 0 B.U.H.,
mankind was faced with extinction by ebola.
The governments of the world decided to sponsor one last epic
novel, to burn everything else so that this one novel would
be mankind's only legacy, so it had better be fucking
good.  That one novel was called Use Hostel.\\
\\
\vspace{1in}``Is it evil to pretend to be evil for an evil purpose?''}}


\begin{document}

\maketitle

\chapter{Welcome to Use Hostel}

If you like to travel for luck, there once was a perfect place for it.
Traveling for luck means putting yourself through hells
where only luck will save you, and doing it in a far
off land.  The perfect place was called Use Hostel.  You pronounce it
like ``Youth Hostel'' with a lisp.  Don't worry, they
won't notice your lisp, it's full of exotic folks, every
cusp of the earth.  By the laws of probability, every author should
risk death to improve his writing, I fancied that's what I was doing
there, `cept the truth is I'd never write shit.

Use Hostel was a tall thin skyscraper in the middle of downtown.
The view was like a desert, if that desert was painted like a city.
Use Hostel was a tower in that desert, with nothing for
miles around.  Tall doesn't mean it was
big.  It was so thin, its total volume wasn't much more
than a spinster's cottage, and that's not even counting her cats.
Instead of stairs or `vators, you'd climb up
a ladder through everyone's rooms.  Instead of a toilet, you'd piss
out the window, I hope you're not scared of heights.
If you took two thousand capsule hotel caps, stacked one on
top of the next, it would be a fancy version of Use Hostel.

Tallman was standing on the Use Hostel roof.  He was balancing on
the heels of his feet, long leather shoes draping over
the edge.  He was smoking an over-long cigarette, laboring to
suck the smoke so far.  Shortman and I were beside him, down on
our haunches, we were not as fearless as he was.  We were spitting
at the city below, it was a typical evening.  Inventing dirty
jokes and passing a bottle `round.  God I miss Use Hostel.

The room right below us, highest room in the `stel, belonged
to the fat woman.  She'd got fat by staying in her room all the time,
and now she was too big to leave.  She depended now on roofcrawlers
like us.  Tallman, for example, would toss her the butts of his
cigarettes, and she'd gobble them up like fries.
As we stood there that evening, we could hear her a-singing.
See, that's how exotic the Use Hostel was, all its customs so
backwards the fat lady sang at the start.

Beneath the fat lady was a mexican named Jesus.  He'd sit
in his room all day singing and jerking off, a smile on
his innocent face.  We didn't really
like him all that much, but we liked his car.  We'd take wild
joyrides in it, banging up the city, taking advantage of our
diplomatic immunity.  Jesus was desperate to make us like him,
he'd always be buying us food, bringing us babes, turning our
water to wine.  We tolerated him cuz of this, but we always made
him sit backseat.

We were actually just about to take the car on the night this
whole thing started.  Not for a joyride but work.  At Use Hostel,
as part of your rent, you gotta do work.  Not hard work, mind you,
and it was well worth it as you'll hear very soon.  Our job that
night was to go pick up a res'.  We always jumped
at the chance to do pickups, we could put in impressions
before the management got their chance.  With Tallman in charge,
we had our own little youth hostel mafia going.  We'd
hook people up with forbidden books, get our hooks in them before they
could make any other connections, then jack up the prices once they
were hooked.  Jesus would say we were fishers of men.
Our businesscards said:  ``You ban it, you buy it.''
We were making enough cash that the city was ours, but
that ain't saying much, the city was everyone's
as long as they were foreign.

Tallman flipped down his fly and squeezed out a piss.
Then with a grunt we were off.  We'd perfected
a technique where we'd go down in freefall, grabbing the ladder at
intervals to stay below terminal `locity.  We waved to our friends
on the way down, Tallman tossed someone a book.  We called our little
operation ``The Library'', Shortman could never say that without face
going crooked with childish laughter, haha.  ``Be sure you don't let your books
overdue,'' Tallman would say, crackling his knuckles through his
mirth.  No-one had actually done it, but the implied threat was
enough for us to assert dominance.  We were dictators crushing
the opposition.

``Amigos, let me come with you,'' said Jesus, he was smoking a shit-joint,
no I mean that literally, it's what people do here.  We couldn't refuse,
cuz he had the keys.  ``I am the way, the truth, and the light,''
he would say, jangling those keys in Tallman's face.  Tallman
would lunge for them with his teeth, snarling and clenching his fists.
Jesus thought it was funny, I think he was autistic myself.
We piled in the car with its busted-out windows.  Held our breaths as
the engine sputtered poisonous gas, then with a blast we were off.
The wind in our hair, Tallman grinning, holding his long cigarette in
his teeth, Shortman and I rough-housing in the front seats.  Jesus sat
in the back jerking off like usual.

We took a shortcut to `Arrivals,' crashing through the runways.  Some
flights were delayed as we mooned `em.  We drove through the terminal
honk-honk-honking the horn, everyone assumed we were janitors.  Imagine
the resident's surprise when we pulled up behind him, screeching to a
stop so close the bumper knocked his briefcase from his hands.  He was
decked in suit and tie, we howled with glee, I quickly made Shortman a
bet, \$20 says no rent for a month.  You'll see what I mean shortly.

No sooner was Tallman out of the car, he was shaking the businessman's
hands, introducing himself in Queen's English and opening his trenchcoat
to reveal hidden bookshelves.  The businessman's eyes lit up all excite-O,
we could tell he was very naive.  Before we even got back
in the buggy, he swiped his card through Tallman's illegal reader, buying three banned
books on credit.  ``Hold your breath,'' I said, as the engine's poisons gasped.
He was so engrossed in his reading he barely more than nodded to Jesus.

Once we got to the `ostel, the manager's son came out, the living image of
Kim Jung Un.  He looked at our friend with disgust, he made no secret he didn't
like capitalists.  ``Welcome to Use Hostel, mang,'' said the kid.  ``Your first
job is to clean up the walls.''

``What?  You're mistaken,'' said the man, ``I've come here to stay.''

``Yeah, of course, man.  You stay in Use Hostel, we gotta use you.  That's what
the name means.  `Less you're here to `subsidize,' that is.''

And that's the way Use Hostel works, dear reader.  We reel `em in blind, these
shakers and movers, they think they'll have an adventure, a romp with hostel
sluts.  Then we rake `em over the grill.  They've never done a day of work in
their life, and they won't be ready to start at Use Hostel.  So we extort a hefty
fee from `em, `subsidizing' is what we call it.  A great cheer went up the whole
length of the hostel, and Shortman passed me a twenty.  Then came the chanting,
`Subsidize! Subsidize!,' followed by the rain of rotten eggshells and grease,
young hearts hazing our new sugar daddy, making him feel properly welcome.

God I miss Use Hostel!


\chapter{Background on Jesus}

Let me tell you what brought Jesus to stay at Use Hostel, it's a funny story.
All his life he'd been known as ``The Healer''.  He healed people, not with a magical
power, neither with medicine, but with good sense and intervention.
To give you an example, imagine you're an old man living alone in a big house full
of memories, and one day Jesus comes knocking on your door asking to show you a sales
catalog.  You let him in and, while giving his sales pitcher, he happens to see the jigsaw puzzles
and electric train sets that belonged to your poor dead son.  He takes the entire day off
and sits with you playing with those old toys, rekindling feelings you never knew
you'd lost.  That's the kind of healing Jesus did.

Well, one day he went to visit his father, and on the way there he got to thinking how he
could help him.  Jesus' father was very short and weak, had been all his life, and bald
to boot.  When you met him he'd point at you with one weak outstretched finger.  You'd never
imagine him in a dance club.  And it occurred to Jesus that that was probably where his
father needed healing most, to remember days of glory.

So Jesus gently guided Dad away from Mom for awhile, and walking together by the river in the park
he said:  ``Dad, tell me about the women you loved before Mom.''

But then Jesus' dad wept.  ``Oh, son, how can I keep this from you any more?
I never loved any woman.  I could never even get a first kiss.''

After admitting that to his son, Jesus's dad actually got weaker.
He limped around with shame ever after.  It was the end of Jesus's good luck streak.
Since shortly after that, Jesus couldn't show his face at any of his
relations', without a warning about his `healing'.

Jesus went through a hard patch.  He wasn't welcome on peoples' roofs, so he
would lurk around spying for anyone patching up leaks, then he'd gather the
throw-away roof-tiles, spend the night under those.

He took up binge drinking, and turned it into bungee drinking.  He ended
up in rehab.  But there's a happy ending, he made one great friend at each
of his twelve step programs.  And each of these friends all told him the same:
``Seek out the Use Hostel.  You are needed there.''

\chapter{They break a banned author out of jail}

You may have heard of jailbreaks where the prisoners dig their way out.
We helped with one of those, but not in the usual way.  Tallman insisted
on doing it in style, so we tapped in to some of that Use Hostel labor,
and we tunneled a way for the car.

The prisoner was a certain author of banned books.  He'd been locked away
for subversive literature and subliteral verses.  You can imagine why
we were interested in having him.  In the cutthroat competitive black
market for books, it was like having a nuclear bomb.  Imagine his surprise
when the car pulled up outside his toilet, the bumper knocking the lantern
off his table.  (We would later find out that it burned down the whole
jail.)  We kicked through what was left of the wall and we napped him.

``What the fuck took you so long?'' he said to Tallman.  ``I've got half a
mind to sue you.''

Tallman playfully ruffled his hair.  ``I'd be worried if I thought you had
half a brain, Doc.''  We waited to hear the prison sirens
blaring before taking off, it was the genius of our plan, use the alarms to muffle
the sound of the engine.

``Hey Yu, I don't think you've met Doc before,'' Tallman laughed, tossing his tie back
over his shoulders to blow like a cape as we burst into the daylight.  (That's how
tall Tallman was, he bought his neckties at novelty costume shoppes, filling the Use Hostel
dumpsters with mutilated vampire gear.)  ``Shortman!  Introductions!''

``Oh man, Doc's the meanest,'' Shortman looked up from his vidya.
``Tell `im about the time you killed all those dudes, Doc.''

``Bastards called me a Philistine,'' said our doctor wiping his specs, they'd gotten
dirty during the jailbreak.

``Ahh, an attack on your literary credentials,'' I said, trying to sound wise.

``What the fuck are you talking about?''  He peered at me through the dirty
spectacles.  ``No, I'm a real Philistine.  Nothing pisses me off more than
when you insinuate things about my people.''

``Where is Philistine, anyway?  One of those Middle Eastern countries?''
Jesus piped up.  We'd all forgotten he was even there, he'd been calmly smoking
his painkillers through the entire operation.

``You ever seen one of those pictures of Israel, and it has, like, this littler,
fragmented country scattered inside it?'' Doc said.

``Oh, Philistine is Palestine,'' I said.

``No, ya moron,'' he gave me a quizzical look like he was checking whether
we were driving on the right side of the road.
``If you look at the tiniest little piece of Palestine, you'll see it's a
perfect copy of Israel, only smaller.  And inside that little Israel, there's
a tiny copy of Palestine, and that's Philistine.  Those are my people.''

``Tell `im about the novel you're workin' on,'' said Shortman.

``I'm travelling the world, visiting its diverse indiginous populations
and pissing `em off,'' said Doc.  ``Pissing on their elephant graveyards
and shitting in their elephant cans.  Mixing up yesterdays ancestor's with
tomorrow's cinammon toast.  See, my goal is to write a novel where every
single line has been cursed.  I didn't think of a title yet, I'll have
to come up with something particularly cursed.''

``You should name it after our youth hostel,'' said Tallman with a laugh.

``Your hostel's too weird, man,'' said Doc with a laugh.  ``If Alice saw it,
she'd look down at Toto and say, `We're not in Wonderland any more'!''

``Hey, you ever write anything about nihilism?'' Jesus asked.

``I'll tell you a story about that,'' said Doc, realizing he had his
specs on backwards he quickly fixed them.  ``I was at an airport once when I got
one of my bursts of inspiration, and right at that very moment, my pen ran out
of ink.  There I was, in a foreign land, flight in fifteen minutes, both sides of
the self-walking platform going the wrong way, and nothing to write down all these
brilliant thoughts pouring into my head.  I'd've shouted them aloud, but they'd have
got me blown up by the TSA.  The three kings themselves couldn't get past security
these days, you know.  To add insult, when they finally did give me a pen, it was to
fill out one of those landing cards.  Imagine this long-bearded Philistine, maniacal
gleam in his eye, scimitar in his belt, feverishly scratching divine revelations about
nihilism on the back of a landing card.  The TSA took the card away, who knows where
it's at now, they probably burned it.  But here's the thing, if the whole ordeal didn't
happen, I wouldn't have this story to tell you now.  So that's kind of my philosophy:
you win some, you lose some, it all evens out in the end.''

``Far out, man,'' Jesus blew a pair of smokerings, one for each lens of the doctor's
eyeglasses.

``Why didn't you use your cellphone, dumbass?'' said Shortman.


``Shit man, they got a road block ahead,'' Tallman spat, he could spit further than
the length of his cigarette, but just barely.

``Eye of the needle man, eye of the needle,'' said Jesus.

``It's cool, I came prepared,'' Doc said.  He rolled up his shirt to reveal suicide
bomber gear.  Shortman and I quickly untied the dynamite, Jesus lit the fuse with his
vaper.  ``{`}The ice did shit with a thunder-fit, and Tallman steered us through!{'},''
said Doc in a ridiculous falsetto-poetic voice, as we blasted our way past, ``That's Poe, by the way.''

``No it ain't, ya boob!''  Tallman kicked him playfully in the shin, the car started
weeving all over the road.  The force of the whiplash sent Doc's glasses flying into the night.
``That's T.S.~Eliot!''

``You can't even spell T.S.~Eliot!''

The air was filled with half-burned pages, swirling around like a tornado.  Doc snatched
at one of them and went ballistic.  ``Fuck man, shit!''  ``What is it?'' I said.  ``They
filled the roadblock with my papers!''  He stood up and shook his fists furiously as his
pursecutors behind him.  I was glad he'd lost his suicide vest.
Jesus absently grabbed one of the pages, crumpled it up into
a tiny little ball, and smoked it.

The car crashed into a ditch, and we all got out and started hunting around for the doc's
glasses.


\chapter{The Doctor is Received}

The first thing Doc wanted with his newfound freedom was to visit
his father's grave.  Easy enough, his father was buried in the Flying
Graveyard.  You've never heard of it?  I'll tell you all about it.  It's the most
convenient option around.  When your loved one dies, you don't need to worry about
transporting the body, the Flying Graveyard comes to you.  When you
want to pay a visit, like our good friend the Doc, you call `em up and make
an appointment.  They'll hover over your roof,
you can grapple aboard.  Where is the Flying Graveyard when it's
not flying, you ask?  LOL, you really are new here.  The Flying Graveyard is always
flying, it was retrofitted from an old Soviet cold war bomber.  Bitch is nuclear
powered.  Rumors say the
graves still hide old warheads, hammer and sickle and all.  You can rest in peace knowing
the statue of Lenin is watching over your dearly departed.  If
you're looking for cheap travel, you can book a ticket on the Graveyard,
it's the cheapest flight around.  You'd better bring a jacket, it's cold in a
graveyard at 30,000 feet.  We launched the passenger option
to make traveling more affordable.  Oh, I didn't mention that?
Yes, the Flying Graveyard is a Use Hostel subsidiary.  Tallman has made it quite clear
if anyone mentions the conflict of interests, he'll make `em wind up dead.

``Don't be fooled,'' said Doc as we looked at the tombstone.
The solemn letters said `Here lies Doc Sr.'  ``Just one of the aces up my shirt.
Watch.''  He rolled up his shirt and produced a combat spade (he hadn't changed
out of his prison outfit).
Jesus grabbed his arm.  ``You can't dig up graves,'' he said.
``You gonna stop me?'' said Doc.  The two got in a scuffle until Tallman pulled Jesus
away.  Jesus kept swinging even as Tallman held him out of reach.
The Philistine dug open the sarcophagus,
and instead of the body, it was full of papers.  ``Government would never look
here,'' he said with a wink, packing the papers under the straps where the
dynamite had been.  ``You see, J., there's no reason to be upset.''  But Jesus was
visibly pissed, he would hold a grudge against Doc a long time.

With no vacancy at Use Hostel, it was decided Doc would share my room.
Then one by one his seventy-two brides started arriving.  I'm sure you've heard of
women falling in love with imprisoned serial killers.  Well it's
worse with imprisoned writers.  We were strapped for space, so each bride had to
room with a Use Hostel regular.  Tallman and
Shortman pulled strings to get the prettiest two.  Every night, one of Doc's
brides would visit, and I'd be obliged to face my chair at the wall.
Then in the morning he'd howl with rage about how she'd deceived him, promised
virginity, how he was cheated, and all that.  When the bride staying with Tallman
came, Doc said:  ``Virgin!  She's slept with every animal in the African safari!
Not only that, every inch tastes like cigarettes.''
The only bride he was remotely happy with was Shortman's.
``She's no virgin,'' said Doc the next morning, rubbing his sore knees,
``but she's pretty damn close.''

Shortly after Doc moved in, we got an interesting visitor.  Shortman and I were sweeping the
sidewalk when a real uptight character showed.

``Can we help you?'' Shortman said with a voice you wouldn't want help from.

``I'm with the GAFMAS,'' he said, flipping his badge at us.  ``The Government Agency For
Making Authors Suffer.''  At his side he held some sort of cage covered with a blanket.
As he spoke, the cage trembled and we heard a sound simultaneously sinister
and adorable.  ``I'm looking for this man,'' he said, and sure enough, where you'd expect
to see his own face, the badge showed Doc's face instead.

``Man, get out of our jello,'' said Shortman.  ``You ain't got no authority here!
Why the hell you think we `spatriated?  You got a warrant?  You probably don't even got a warranty.
Go home, why don't you leave us to the local authorities.  That's what they're paid for!''

``The doctor's not in,'' I chimed.  ``If this is a medical emergency, please dial F-U-C-K-Y-O-U.
Doc's too important for plastic surgery.  If you're here for lipo, you better
check the exchange rate on fat.  You're in the wrong neighborhood, friend, this ain't
Kaiser Permanente.  You can still call us Kaiser though.''  Then Shortman tugged on a bell, and
a crowd of Hostellers chased the agent away, sent him crawling and crying to the nearest
bus stop.  Burnt like a book.


One evening the Doc and Tallman were out on the town and I was guarding the fort.
In came Tallman's girl, dressed like a concubine.  She sat on my lap and asked if
I'd like to share her sleeping bag tonight.  I got real excited to
snuggle up so tight with such a crunchy mama.  But the sleeping bag was so loose it was
more like sharing a tent.  In fact it was so loose I tossed and turned fitfully.  At one
point I woke up soaking, afraid the hostel was burning, it was the cigarette smell.
The girl had an unamused look on her face.  ``When is Tallman getting back,'' she said boredly.
A few weeks later she missed her period.  Doc was furious, he's
particular about grammar.  Fortunately Tallman had a novel method of fixing missed
periods.  Picture a stork flying along, and someone sticks a long cigarette through a tube
into its beak.  This stork, it inhales the smoke, and this happens day after day, month
after month.  Eventually the stork delivers a sickly baby, weak and blinking with lung
cancer.  The surgeons spare no expense, but who can cure cancer?  As for the
umbilical cord, Shortman keeps that, don't even ask what he does with the thing,
for all I know he jumps rope with it.
Shortman has a saying:  ``Life is nothing but a drug called \emph{umbilical
cord}.''  Doc laughs and says:  ``I might be the only man who still feeds through the
umbilical cord.  Any time I've got writer's block, mom sends me her corny story ideas, it's
the finest protein for my babyish brain.''


To ensure the doctor's productivity, we set him up with a kind of hamster
wheel.  Instead of revolving it with your feet, you revolve it with your fingers.
The faster you type, the faster it spins.  The Doc would sit in there for hours,
typing furiously.  It was so cute the way he thought if he could just go
fast enough he'd get somewhere.  Tallman was thrilled with the output it
generated.  Me, I wasn't so Happy Meal, the squeaking kept me up late.
One day when Doc was out clubbing with Tallman, I couldn't help give the wheel
a try.  I was such a wretched writer, the thing went backwards!


\chapter{The Amateur Church}

The management was worried about morals around the hostel, so they asked us to build `em a church.
We rounded up the best-traveled men staying with us, sorted `em by length of the beard.
Tallman passed a spiral around,
``Everyone write down what you know about churches.''

``Does anyone have a Bible?'' asked Shortman.

``I've got The Brothers Karamozov,'' offered Old Ivan.  Old Ivan was a sad specimen,
always wanted to be a barber, but no-one would hire an old Russian barber, so he had to work at noodle shops, abusing his
proud hair-cutting tools to cut ramen and spaghetti.

``Good enough,'' said Tallman.  ``Anyone else?''

I picked up Dostoevsky and flipped through the holy work.  ``Ooh,'' I said, ``can I be the crazy priest
who hallucinates demons?''

Doc supplemented the Brothers with a copy of ``Before the Law'' torn out of the novel around it.  As well as some
pages of his own.  The author would leapfrog in his grave if he knew the way we were using it.

``Man, has any of us even pushed foot in a church?'' asked Old Ivan impatiently.

``I broke up a wedding once,'' Shortman said.  He showed us the rings on his fingers.

We didn't have any holy ground for a church, so we built it out sideways, jutting out from the hostel.
An engineer would have taken one look and burned up his license.
Then we got in an argument.  If the church was sideways, which way should we put the cross?
A right angle would make it too phallic.  But if it was parallel to the hostel, it would be perpendicular
to the church.  In the end we struck a compromise, hang it upside down.
Tallman liked it, he would go there on calm days, hang inverted from the cross-arms like monkey-bars.
Smoking a longass cigarette, it was hard to say which was longer, the cross or the cigarette.
With his nose below his mouth he would inhale the smoke right back in where it came from.
It was a smoke ourobouros.

How did we get the cross there, you ask?  We asked Jesus, of course.  Crafty bastard found this dis-assemblable
IKEA cross.  He carried it up at his leisure.  Some screws went missing, we had to shorten the
right arm of the cross, make it a bit asymmetric.

It was too awkward for plumbing, so when you wanted baptism, you had to lug the water up yourself.
Fourty gruesome floors up the ladder, with Shortman and Tallman whipping your back.  After you were done we'd throw
out the bathwater, one time we accidentally threw a baby out with it.  To cover up the incident,
we made it a regular ceremony.  We hadn't planned on child sacrifice at the start, but it's better
than murder.  ``A good writer kills his babies,'' as Doc would say.

Doc's virgins were especially excited about the church.  It was somewhere they could sleep aside from
the cramped rooms.  As soon as word got around, the church would be packed with Use Hostel men,
bothering the brides to no end.  They would all lie around amid the carpentry tools, bras and panties draped
over the cross's arms, we had to chase them out to get any building done.

In the later stages of construction, Doc misplaced one of his explosives, blew up part of the wall.
There in the rumble we saw a pair of ancient scrolls.  They'd been hid in the Use Hostel wall
since before antiquity.  ``The original scriptures!'' Doc exclaimed, fingers in
his mouth with disbelief.  Tallman picked up the scrolls and opened `em.  ``No such luck Doc,'' he
said, ``It's the Brothers and the Law.''

When we were done with it, the management didn't like the color.  In the end we had to build an identical
copy on the opposite wall.  On the plus side, if you looked at the hostel from afar, it looked
like a cross by itself.

\chapter{A job at Use Hotel}

The manager of Use Hostel had a brother in the next city over.  The brother ran a joint called the Use Hotel,
a luxury resort for the wealthy.  Always bustling with Smiths keeping up with each other.
One day this brother needed manual labor, so he called up the
Use Hostel and Tallman volunteered us.  The Use Hotel manager promised a week's board and room.

Disembarking at Use Station, we couldn't see the end of Use Hotel to either the left or the right.
On the contrary, the hotel was shortest in the middle, growing taller at either pole.
You know how airports have those self-walking platforms?  Use Hotel had those for cars.
``Would've been nice to have one of those in our prison break,'' said Doc.
``For seven's sake, there's no pleasing some people,'' said Tallman.
There were car escalators too, some of the tenants insisted on parking their car
in their room.  Rambunctious kids would drive the car up the down escalator or down the
up escalator, driving their parents bonkers.

The receptionist was a professional Ronald Reagan actor.  ``Who the what's it?'' he said, looking at us
with confusion.  ``It's okay, Ronny,'' said his nurse, ``remember, you're a receptionist at Use Hotel now.''
He twisted his mouth, struggling with memory.  ``Are you the gunrunners?'' he said.

``We're from Use Hostel,'' said Tallman, ``we volunteered for day labor.''

``You don't look Mexican to me,'' said Ronny, carefully leafing through the ledger.  ``Where's Nancy?
I've got a state of the union in ten minutes, where the hell is that cunt?''

``Looks like it's time for Ronny's nap,'' said the nurse, carefully leading him away.
She came back with an over-full adult diaper, we all held our nose.  She looked at the trashcan on
one end of the lobby, she looked at us on the other.  A moment of indecision.  Then she walked to us,
setting the diaper down on the counter and daintily covering it with a page from the ledger.
``Sorry about that,'' she said, ``Alright, we were expecting you, here are your nametags.''

It was more like wearing a barrel than wearing a nametag.
At Use Hotel, nametags were very important, to let people know who you are.  The lower your lot in life,
the bigger the tag, to make room for more info.  We were such nobodies, most the space was
advertisements, I guess they do `subsidies' at Use Hotel too.  If you were real rich, like
an oil sheik from Serbia, they'd give you a nametag smaller than a novelty miniature postage stamp.
You'd stand around gloating while awe-struck people craned their necks and leaned in real close trying
to read it.

``There's been a mixup with your room,'' said the nurse.  ``We're all out of bedpans, so we've upgraded
you to an executive suite.''


When we opened the door it was like opening the door to a city, if that city was spaced out like a desert.
The room had its own entrance lobby, complete with doormen and receptionists, bellboys and liftboys,
accountants to take care of their paychecks, economists to take care of the accountants, professors to
take care of the economists, in short it really was a city, but it was so spatious that if you wanted
to walk from the baker to his bread-boy, it would take you an hour.

A shiny stretch limo pulled up to take us through the living room to the bedroom.
The limo itself was spatious and luxurious, not a city per se but maybe a hamlet.
``To be or to be not,'' said Doc with a chuckle.
Complimentary escort girls lounged in the limousine hot-tub.  They were naked except for their nametags,
which were just big enough to cover the important parts.  Doc wasted no time burying his face in a big pair
of titties, ``A writer needs his muse.''  Soon milk was running down his chin, he was a happy cat.
Jesus helped himself to the limo's complimentary hookah.  ``Can't be a fisher of men without a hookah,''
he said.

``Hey guys, I've got an idea,'' said Shortman.  Then to the driver:  ``Hey man, we've got this job we've gotta do while
we're here.  Lots of manual labor and stuff.  Think you can take care of it?''

``Of course, sir,'' said the driver in a perfect British accent.  He had attended the Harvard School of Conveyances,
where he authored a PhD on the subject of transporting Eastern European princesses.
The dissertation won awards and was well-cited, eventually leading to a
publication in Nature.
Lesser professors had even written dissertations on the art of transporting this driver around.
He pulled over and made a quick phone call.  ``No need to worry about it, sir.  My guys already know the job
you're talking about.  In fact, we anticipated you'd ask it: the work's already done.''

We all high-fived Shortman (Tallman had to do it under-handed).  The limo stopped as it arrived at the destination,
the door to the bedroom itself.  It was protected by a moat, the driver pushed a button to lower
the drawbridge.  Beyond the moat, the bedroom wall was a replica of the Great Wall of China,
I guess they gave us the oriental room.
We piled out of the car, a little tipsy from the car-bar.  Tallman slipped the driver a
coin to show our appreciation.  The girls waved from the hot-tub, exhorting us to come back soon.
We watched as the car drove off to the crusher, it was the policy here that no limo be re-used a second time.

The bedroom itself was an indoor beach.  It had pristine white sand and stretched as far as the eye
could see.  Tallman crouched, wetted his finger, tentatively licked a pinch of the sand.
``This is no sand,'' he said, ``it's cocaine.''
Instead of sofas there were beach-chairs.  A giant outdoor movie screen looked like
it would fit in a drive-in theatre, if the IMAX had drive-ins.

As for the beds, they were aboard a massive luxury cruiser.
We went aboard and promptly passed out on the soft bedding, we were really pooped from our ride on the Use Train.
That idiot Jesus tripped over the anchor chain, and while we were sleeping, the ship went adrift.
By the time we woke up, there was no land in sight.  We were lost at sea.

There wasn't much food aboard.  Most of the larder was taken up with long cigarettes.  Tallman made good use of them,
climbing the crow's nest to send out smoke signals.  Fortunately the seawater was potable,
although it had a bit of a chlorine taste.  It was disgusting to drink,
they kept it heated to room temperature.

Day after day, we paced the decks, stomachs roaring with hunger.  ``As idle as a painted shit upon a painted
ocean,'' said Doc in despair.  Our big huge nametags are all that saved us,
we were able to gnaw at them for nourishment, if we'd been fatcats we'd've starved.

By day, the heat of the articial tanning-bed sun beat down on us.
By night we were able to navigate by the artificial stars.  Doc did some calculations.  ``If that over there's Venus,''
he said, ``we're somewhere in Antarctica.''

On the last day of our reservation,
when all hope was lost, Tallman spotted an island.  We lowered the lifeboats and pedalled ashore.  The ship sank behind us,
hotel policy just like the limo.
It was a tiny desert island, not even so much as a palmtree, but sitting on a pedestal there was a white hotel phone.
``Use Hotel, front desk speaking.  What?  Again?!  Do you know how many guests get lost in there?  Hang on,
we're sending help.''

In a few minutes, a private jet came to our rescue.

\chapter{They burn a city library}

The contents of this chapter are important, and I wanted to get every detail right.
So I'm transcribing it all straight from Shortman's journal, to make sure none of the facts
are embellished by the decay of memory.

The time had come to take a bite out of our competition.  The city library was poaching customers from us
with their shitty unbanned books.  How anyone could stand that boring tripe is beyond me, but fools make the
best customers, so a good businessman can never really understand his own customers.

``Isn't burning a library a bit extreme?'' asked Jesus.

``If the books were important, they would've been banned,'' Tallman said.

The city library was shaped like a ship.  It was ripped off the Library of London.
The lower floors were long like a hull, and the higher floors were narrower, so that part of the roof
of the lower floors served as ship'sdeck.  The highest floors formed a tower, painted to look like a
smokestack.  Three great sails, with three crow's nests, were purely for decoration.  By chance, the library
was in the middle of a grand exhibition.  In the discovery of the century, archaeologists had uncovered
a treasure trove of books, a perfect duplicate of the original Library of Alexandria.  All these priceless
works were on display at the city library, for one week only.  We smiled looking at the packed crowds,
a perfect screen for our plan.

We figured it would be best to start the fire from the inside out.  So Doc penned some books with his
patent pending exploding ink.  In the interest of time, these books were the trashiest, most formulaic of
romance novels.  He wrote a dozen of them in one sitting.  Books like ``Wolfshoulders of Cambridge'',
about a wealthy muscle-bound scholar with ravenous wolves for shoulders, and how he was tamed by Madame
Lindsey of the Sigma Lambda Tau sorority.  We had no trouble sneaking them into the library, the patrons
love garbage like that so the library lapped `em right up.  In fact the library put them on display beside
ancient Alexandrian works like Euclid's ``Conics''.

Our major concern was that people would haul books out of the library before they could ignite.  So Tallman,
Doc, and I, we covered the three exits to the library with our trojan horses.  Three giant trojan horses,
with us hidden inside.  The library was happy to have `em parked by the exits, they thought they were part of
the whole theme.  Little did they know we were waiting inside with bullhorns, to yell at anyone taking out
books.  Doc, immature guy that he was, couldn't help but giggle every time anyone said the word ``trojan'',
then he'd whip out some juvenile condom joke.  It was completely inappropriate given the grave nature of our
work that day.

As for Shortman, his job was to sew chaos.  The main lightsource was the adjacent lighthouse.  This, too,
had been dug up by archaeologists, it was a previously unknown identical twin and contemporary of the Lighthouse
at Alexandria.  Shortman scaled the walls (we were all very good at this from Use Hostel) and, with the help of
Old Ivan, absconded with the lighthouse lamp!  Later we would plant it on the roof of Use Hostel, making
the `stel a shining beacon visible for hundreds of miles.

As soon as the light blinked out, Doc pushed a button and his trashy romances burst into fireballs.  The
ancient scrolls beside them were dry and flammible, and in no time at all, we had a glorious bonfire going.
Patrons and tourists rushed out in droves, we didn't care about them.  But as soon as we saw someone holding
a book, we'd give `em a roar through the trojan megaphones.  ``You in the bluejeans!  Drop the Plato!''
``You with the trenchcoat!  Yes, you!  Open it up!  Hah, thought so!  Throw those scrolls back in the flames,
and no funny stuff!''

A Spanish soldier made a mad dash for it.  I cursed into the walkie talkie, ``We've got a live one!  Cover me,
I'm going after him!''  I dropped through the trapdoor in the bottom of my horse, dashed after the man.
Jesus opened fire from a nearby high-rise, his machine gun making sure no-one would try to go out my exit while
I was away.

The spaniard was faster than me, but no-one knows the streets around Use Hostel as well as I do.  Soon he ran into
a dead end.  ``Alright, nice try, fork over the book.  What is it, anyway, you sure seem hellbent on saving it!''
I grabbed the stack of books from him.  ``What the hell?  What language is this even?''

``Aztec, sir,'' he said, ``please don't shoot me!  I have a family!  This one here's Mayan.''

``I didn't know there were New World books in the library,'' I said.

``We were trying to keep them hidden from the public until scholars could photograph them properly,'' said the
soldier.  ``A whole floor of `em burst into flames, I grabbed these to save what I could.''

``If people want books, tell `em to visit Use Hostel,'' I barked, ran back to my horse.  I tossed the American
literature through a window into the inferno inside.

Inside the library, Head Librarian Smith was holed up on the bridge, holding an emergency meeting with his officers.

``This library's going to sink in less than two hours,'' said the chief architect.

``Man the lifeboats,'' said the head librarian.

``Sir, we don't have enough boats.''

``May god have mercy on our souls.  Women and children first.''

Then began the frantic lowering of lifeboats from the deck of the library.  Boats were so packed that the flames
came up to the very rims.  A couple of the collapsible boats, launched right as the great library was splitting in
two, flipped upside down in the flames.  I saw a mass of men frantically clinging to these, flames all around `em.

The last thing we saw of the library before it vanished under the sea of fire was the three lookouts, standing in
the crows nests faithfully until the very end.


%OUTLINE

%1. Welcome
%2. they burn a city library
%3. they break a banned author out of jail
%4. they're attacked & beaten by crufifix-wielding monks  (Longman, Stoutman, and Mi)
%5. Tallman tries to commit suicide
%6. Yu and Mi randomly meet at a club, end up sleeping together beneath the only tree in the city
%6. they follow the monks and find a city library volcano hq in The Mountain
%7. jesus douses them with holy water, they devise a plan to defeat the monks
%8. their plan fails, the monks beat them again. then it transpires the monks are really just jealous that use hostel has its
%    own private church.  the monks join onto Use Hostel as deacons in the church
%9. they use the mustard seed to blow up The Mountain.  unexpected consequence: all books become unbanned
%10.Tallman smokes the Use Hostel.
%11.Where the use hostel once stood, a magnificent tree grows

%Random ideas:
%* they have an assistant who burns unbanned books
%* after they blow up the mountain, the city library unbans all books, hence the final chapter


\end{document}
